---
title: "Data Visualiaztion Final Report"
author: "Saint Roger Bountsebe Eboueme"
date: "11/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggrepel)
library(tidyverse)
library(socviz)
library(dplyr)
library(knitr)
library(broom)
data <- read_csv('/Users/saintroger/Documents/Data_viz/Data/Building_Permits.csv')

```

## Final Presentation
Analyst: Saint Roger
Client: Nick

## Tables Of Content

- Providing Context
- Background on the data 
- Question asked by the client
- Methods and Exploration
- First plot
- Second Plot 
- Third plot
- Recommendation 


## Context of analysis
- Accurate planning


## Background on the data
Brief talk about the sources of the data and what it means

- San Francisco department of buildings inspection 
- Important Columns: `duration_1` ~ `num_unit_added` +`Proposed Use` + `Permit Type` + `Estimated Cost`


## Question

What factors have a significant impact in the duration it takes to issue a permit?


## Methods and Exploration

- Create 2 new variables
```{r}
data_new <- data %>% 
  mutate(duration = as.Date(`Issued Date`) - as.Date(`Filed Date`) ) %>% 
  mutate(num_unit_added = `Proposed Units` -  `Existing Units`)
```

```{r processing, include=FALSE}
data_new <- filter(data_new, duration > 0)
df <- data_new %>% 
  group_by(`Neighborhoods - Analysis Boundaries`, `Permit Type`) %>% 
  summarize(mean_duration = mean(duration, na.rm = TRUE),
            prmt_tp_perNeigh = n())

df <- na.omit(df) 
```

- Group by Neighborhood and Permit Type
- Linear Regression ` lm(formula = `duration_1` ~ `num_unit_added` +`Proposed Use` + `Permit Type` + `Estimated Cost`, data =data_new)`


## First Plot

```{r fig.width=12, fig.height=8, echo=FALSE}
p <- ggplot(data = df, 
            mapping = aes(x =`Neighborhoods - Analysis Boundaries`, 
                        y = `Permit Type`))
 p + geom_point(aes(size = as.numeric(mean_duration))) +
   coord_flip()+
       labs(
    x = NULL,
    y = "Permit Type",
    title = "Average wait time of the different type of permit across all SF Neighborhood ", 
    caption = "Plot for presentation") 
figure_3 <- ggsave("Figure3.png")

```

## Second plot

```{r figure2, fig.width=8, fig.height=5, echo=FALSE}
na.omit(data_new)
p <- ggplot(data = df, 
            mapping = aes(x =as.numeric(`mean_duration`), ##f6d908  "#d6c054"  #good yeallo: #DEB828  #good gray: bababa
                        y = as.numeric(`Permit Type`)
                        ))
 p + geom_density_2d_filled(alpha = 0.8, show.legend = FALSE)+
     scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8) ,labels = c("", "","additions alterations/repairs", "sign - erect", "", "", "", "otc alterations permit"))+
    labs(
    x = "Average Duration",
    y = "Permit Type",
    title = "Type of permits: Their occurences and the average waiting time", 
    subtitle = "How does it take to deliver different permit types? ", 
    caption = "This density plot shows the average number of days it takes to issue a different type of permits",
    legend = FALSE
  )
 figure_2 <- ggsave("Figure2.png")

```


```{r, include=FALSE, echo=FALSE}
data_new$duration_1 <- as.numeric(data_new$duration, units="days")
out <- lm(formula = `duration_1` ~ `num_unit_added` +`Proposed Use` + `Permit Type` + `Estimated Cost`, data =data_new)
out_conf <- tidy(out, conf.int = TRUE)
out_conf %>% round_df()
```

## Third Plot 

```{r Figure3, fig.width=12, fig.height=6, echo=FALSE}
out_conf <- tidy(out, conf.int = TRUE)
out_conf %>% round_df()

#using this let's select the value at the 5 % percent significant level. 
old <- theme_set(theme_bw())

subset_out_conf <- out_conf %>% 
  filter(statistic > 2 | statistic < - 2) 

#No need to have the intercept displayed
subset_out_conf <- subset_out_conf %>% 
   filter( term != "(Intercept)")

 #not sure out to select the 3 start only so I look at the statitic value
more_signif <- subset_out_conf %>% 
  filter(statistic > 3.8 | statistic < -4) #95
           
p <- ggplot(data = subset_out_conf, 
            aes(x = reorder(term, estimate), 
             y=estimate, 
             ymin = conf.low, 
             ymax = conf.high))
p + geom_hline(yintercept = 0, color = "gray20") + 
  geom_pointrange() + 
  geom_pointrange(data = more_signif, aes(x = reorder(term, estimate), y=estimate, color ="95% level of significance ")) +
  coord_flip() +
  scale_x_discrete(labels = rev(c("PU antenna", "nursery(floral)", "moving & storage", "parking lot", "lending institution", "parking_garage public",  "Residential Hotel", "Food/beverage hndling", "Estimated Cost", "Office", "Permit Type", "massage parlor")))+
  labs(
    x = NULL,
    y = "Value Of Estimators",
    title = "Variables with significant impact on construction permit duration in san francisco", 
    subtitle = "How much impact does each variables here have on the duration of a permit to be issued?", 
    caption = "Data from the San Francisco hosuing"
  )+ theme_set(old) +
  theme(
        text = element_text(family = "Times"))
figure_1 <- ggsave("Figure1.png")

```


## Recommendation

Important variables:  
Proposed Used  
Permit Type  
Massage Parlor  
Build Offices   
